Instructions for developing new pages for the MarineOmics webpage

### 2023-12-15 ADMIN_01_submissions_instructions.Rmd
added a bit to submisisons instructions page about makign sure to compile a list of dependencies to render .Rmd for our conda environment that I'm starting to build

### MarineOmics publishing process
#### Content development and review process
1. Initiation: The potential contributor contacts the website manager via email  (jasonjohns[at]ucsb.edu) or the discussion forum with an idea.
<br>
2. Development: Meet with the website manager, Katherine Silliman and/or Sam Bogan (Working Group Co-leaders). <br>
    + All active members will be invited to be involved in the review process. <br>
    + The contributor presents their idea for new material to any involved working group members. <br>
    + There will be regular meetings (frequency decided by those involved) with the website manager, Katherine Silliman and/or Sam Bogan, and any other participating members for progress updates and support. <br>
3. Review: Full drafts of content will be reviewed by the website manager, Katherine Silliman and/or Sam Bogan, and at least one other active MarineOmics member assigned to the project.

@@

After following these step, you can cite them in the RMarkdown document.
Let's say you have a paper you want to cite by LastName et al. 2023 and
the paper's ID in your .bib file is 'LastName2023-xy'. We can reference
this paper in-text by adding [\@LastName2023-xy] to the end of a
sentence. This will produce a reference such as the one below for Tripp
et al. 2017.

*syntax in .Rmd text **(not in a code chunk)***:

@@

@@

## References

>>>>

### MarineOmics publishing process
#### Content development and review process
1. Initiation: The potential contributor contacts the website manager via email  (jasonjohns[at]ucsb.edu) or the discussion forum with an idea.
<br>
2. Development: Meet with the website manager, Katherine Silliman and/or Sam Bogan (Working Group Co-leaders). <br>
    + All active members will be invited to be involved in the review process. <br>
    + The contributor presents their idea for new material to any involved working group members. <br>
    + There will be regular meetings (frequency decided by those involved) with the website manager, Katherine Silliman and/or Sam Bogan, and any other participating members for progress updates and support. <br>
3. Review: Full drafts of content will be reviewed by the website manager, Katherine Silliman and/or Sam Bogan, and at least one other active MarineOmics member assigned to the project.
4. Publishing: Final versions of content will be published with the help of the website manager. Please have a list of all software dependencies necessary for your .Rmd to be rendered so we can add it to our MarineOmics conda environment.

@@

After following these steps, you can cite them in the RMarkdown document.
Let's say you have a paper you want to cite by LastName et al. 2023 and
the paper's ID in your .bib file is 'LastName2023-xy'. We can reference
this paper in-text by adding [\@LastName2023-xy] to the end of a
sentence. This will produce a reference such as the one below for Tripp
et al. 2017. <br>
<br>
*syntax in .Rmd text **(not in a code chunk)***:

@@

You can also add hyperlinks to each in text citation that direct to the References section at the bottom of the page. The in text citation keeps its normal format, but with brackets added around the parentheses. Directly after the citation (also in parentheses) is the '#' link to the References section: (#refs) in this case.<br>
<br>
**.Rmd**: [(\@Tripp2017-cp)]\(#refs) <br>
**rendered html**: [(@Tripp2017-cp)](#refs) <br>
<br>
At the bottom of the .Rmd, where the '## References' heading is, we have a '{#refs}', which creates the target for all links with '(#refs)'. It looks like this on the .Rmd:<br>
## References {#refs}

@@

## References {#refs}
